Two applications of logic programming to Coq

### 2020-11-07 papers/types2020/intro.tex
Various minor updates, mostly to normalize the name of some FPC predicates.
Uniform spelling of Coq-Elpi

Before we can present these examples, we first highlight the rather
striking differences in notions of computing and reasoning that arise
on each side of the \texttt{coq-elpi} API.   We will also present a quick
summary of the key proof theory concepts that are used by our example
applications.

@@

% LocalWords:  Sacerdoti Coen Tassi Elpi Teyjus Felty LCF tacticals
% LocalWords:  intuitionistic elpi coq MetaCoq

>>>>

Before we can present these examples, we first highlight the rather
striking differences in notions of computing and reasoning that arise
on each side of the Coq-Elpi API.   We will also present a quick
summary of the key proof theory concepts that are used by our example
applications.

@@

% LocalWords:  Sacerdoti Coen Tassi Elpi Teyjus Felty LCF tacticals
% LocalWords:  intuitionistic elpi coq MetaCoq et al
